Make manuscript figures

### 2021-11-17 scripts/R/make_manuscript_figures.rmd
add more descriptive figure for simulation model

>>>>

OU process for simulation setup figure
```{r}
# Simulate many OU trajectories along tree
generate_trait_trajectory <- function(v0, alpha, theta, sigma, N_steps) {
      POUMM::rTrajectoryOU(
            z0 = v0,
            t = 1,
            alpha = alpha,
            theta = theta,
            sigma = sigma,
            steps = N_steps)
}

# Generate tree
set.seed(10)
tree <- ape::rtree(n = 4)
tree$edge.length <- tree$edge.length * 6
node_times <- POUMM::nodeTimes(tree)
edge_colors = RColorBrewer::brewer.pal(n = 4, name = diverging_palette)

# Define OU process
scale_factor <- 10  # 1000
v0 <- 4.5
theta <- 4.5
alpha <- 60 / scale_factor
sigma <- 2 / sqrt(scale_factor)

set.seed(30)
# Generate OU trajectory for each edge on tree
for (j in 1:nrow(tree$edge)) {
      from = tree$edge[j, 1]
      to = tree$edge[j, 2]
      N_steps = round(tree$edge.length[j]*scale_factor) - 1
      print(paste(N_steps, "steps on branch", j))

      trajectory <- POUMM::rTrajectoryOU(
            z0 = v_nodes[from],
            t = 0.0001,
            alpha = alpha,
            theta = theta,
            sigma = sigma,
            steps = N_steps)

OU_plot <- ggplot(
      data = traceplot,
      aes(x = time, y = v, group = lineage)) +
      geom_line(size = 1.25) +
      theme_void()

#TODO: I have no idea how the edge coloring works, this is a really shitty hardcoded soln
# tree_data = data.frame(node = c(1, 2, 3, 4, 5), color = c(edge_colors[2], edge_colors[3], edge_colors[4], "blue", edge_colors[1]))

tree_plot <- ggtree::ggtree(
      tree,
      ladderize = F,
      size = 1.5)

# Align OU and tree plots
aligned_plots <- align_plots(OU_plot, tree_plot, align = "hv", axis = "tblr", rel_heights = c(3, 1))

svglite::svglite(filename = paste(FIGDIR, "ou_process_for_simulation_figure.svg", sep = "/"))
      ggdraw(aligned_plots[[1]])
dev.off()

svglite::svglite(filename = paste(FIGDIR, "tree_for_simulation_figure.svg", sep = "/"))
ggdraw(aligned_plots[[2]])
dev.off()
```
